---
title: "p8105_hw4_xz2678"
author: "Xinyan Zheng"
date: "October 26, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
library(tidyverse)
library(janitor)
library(ggridges)
library(ggthemes)
```

```{r}
data_pups <- read_csv("./FAS_pups.csv")%>%
  clean_names()%>%
  gather(key= PD_outcome, value= days, pd_ears:pd_walk)
```

Load and wrangle the dataset. After combining PD ears, PD eyes, PD pivot, PD walk 4 columns into one single variable named **pd_outcomes**, we get the final dataset with `r dim(data_pups)[1]` observations. 

```{r}
data_pups %>% 
  filter(!is.na(days)) %>% 
  ggplot(aes(x = days, y = PD_outcome)) + 
  geom_density_ridges(scale = .85)+labs(
    title = "Ridge Plot for the Post-natal Days of Each Developmental Landmarks ",
    x = "Post-natal Days",
    y = "Developmental Landmarks"
  )
```

Analysis: According to the plot, the PD eyes have the longest post-natal days while PD ears have the shortest post-natal days. Respectively, the post-natal days for PD ears, PD eyes, PD pivot, PD walk are clustered around 4 days, 7days, 9days,13days.
